\documentclass{article}    

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
 
\usepackage{amsmath, amsthm,amssymb}
\newtheorem{theo}{Theorem}
\newtheorem{lem}[theo]{Lemma}


\input{commands.tex}

\begin{document}

% \begin{lem}
% \label{lem:NsubsetAbeta}
% Let $\A\subset \Zbeta$ be an alphabet such that $1\in \A[\beta]$. If the set $\A[\beta]$ is closed under addition, than $\NN\subset \A[\beta]$.
% \end{lem}
% \begin{proof}
% For any $n\in\NN$, the sum $1+1+\cdots +1=n$ is in $\A[\beta]$ by the assumptions.
% \end{proof}




\begin{theo}
\label{thm:betaExpanding}
    Let $\omega$ be a complex number and $\beta \in\Zomega$ be such that $|\beta|>1$. Let $\A\subset \Zomega$ be an alphabet. If $\NN\subset \A[\beta]$, number $\beta$ is expanding.
\end{theo}
\begin{proof}
For all $n\in\NN$ we may write 
    $$
    n=\sum_{i=0}^{N}a_i\beta^i\,,
    $$
    where $N\in\NN$ and $a_i\in\A$.
    
    Set $m:= \max\{|a|\colon a\in\A\}$. We take $n\in\NN$ such that $n>m$. 
    Since $|a_0|\leq m<n$, there is $i_0 \in \{1,2,\dots,N\}$ such that $a_{i_0}\neq 0$. Thus, $\omega$ is an algebraic number as $a_i\in\A\subset\Zomega$ and $\beta$ can be expressed as an integer combination of powers of $\omega$. Therefore, $\beta$ is also an algebraic integer.
    
    Let $\beta'$ be a conjugate of $\beta$.  
    Since $\beta\in\Zomega\subset\QQ(\omega)$, there is an embbeding $\sigma: \QQ(\omega)\rightarrow \CC$ such that $\sigma(\beta)=\beta'$. Now 
    $$
    n=\sigma(n)=\sum_{i=0}^{N}\sigma(a_i)\beta'^i\,.
    $$
    Set $m':= \max\{|\sigma(a)|\colon a\in\A\}$.  Assume that $|\beta'|<1$. For all $n\in\NN$, we have 
    $$
    n=|n|\leq\sum_{i=0}^{N}|\sigma(a_i)|\cdot|\beta'|^i \leq \sum_{i=0}^{\infty}|\sigma(a_i)|\cdot|\beta'|^i \leq m'\frac{1}{1-|\beta'|}\,,  
    $$
    which leads to contradiction. I.e., all conjugates of $\beta$ are at least one in modulus.
    
    If the degree of $\beta$ is one, the statement is obvious.  Therefore, we may assume that $\deg \beta \geq 2$. 
    
    Suppose  for contradiction that $|\beta'|=1$ for the conjugate $\beta'$  of $\beta$ such that $\beta\neq\beta'$. The complex conjugate $\overline{\beta'}$ is also conjugate of $\beta$. Take any conjugate $\gamma$ of $\beta$ and the embbeding $\sigma': \QQ(\beta')\rightarrow \CC$ given by $\sigma'(\beta')=\gamma$.
    Now
    $$
    \frac{1}{\gamma}=\frac{1}{\sigma'(\beta')}=\sigma'\left(\frac{1}{\beta'}\right)=\sigma'\left(\frac{\overline{\beta'}}{\beta'\overline{\beta'}}\right)=\sigma'\left(\frac{\overline{\beta'}}{|\beta'|^2}\right)=\sigma'(\overline{\beta'})\,.
    $$
    Hence, $\frac{1}{\gamma}$ is also conjugate of $\beta$. From the previous, $\left|\frac{1}{\gamma}\right|\geq 1$ and $|\gamma|\geq 1$ which implies that $|\gamma|=1$. We may set $\gamma=\beta$ which contradicts $|\beta|>1$. Thus all conjugates of $\beta$ are greater then one in modulus, i.e., $\beta$ is an expanding algebraic number.
\end{proof}



\begin{theo}
Let $\A\subset \Zbeta$ be an alphabet such that $1\in \A[\beta]$. If the extending window method with the rewriting rule $x-\beta$ converges for the numeration system $(\beta, \A)$, than the base $\beta$ is expanding and the alphabet $\A$ contains at least one representative of each congruence class modulo $\beta$ in $\Zbeta$. 
\end{theo}
\begin{proof}
The existence of an algorithm for addition which is computable in parallel implies that the set $\fin{\A}$ is closed under addition. Moreover, the set $\A[\beta]$ is closed under addition since there is no carry to the right when the rewriting rule $x-\beta$ is used. For any $n\in\NN$, the sum $1+1+\cdots +1=n$ is in $\A[\beta]$ by the assumption $1\in \A[\beta]$. I.e., $\NN\subset \A[\beta]$ and thus the base $\beta$ is expanding by Theorem~\ref{thm:betaExpanding}.

In order to prove the second part, we have to show that for every $x=\sum_{i=0}^N x_i \beta^i \in\Zbeta$ there exists $q\in\Zbeta$ and $a\in\A$ such that $x=a+\beta q$. We can suppose that $x_0> 0$ because $x=x+k\cdot p(\beta)$ where $p$ is minimal polynomial of $\beta$ and  $k\in\ZZ$ is such that $x_0+k\cdot p(0)>0$. Since $\NN\subset \A[\beta]$, we have
$$
x_0=\sum_{i=0}^{n}a_i\beta^i\,,
    $$
    where $n\in\NN$ and $a_i\in\A$. Now
    $$
    x=\underbrace{\sum_{i=0}^{n}a_i\beta^i}_{=x_0} + \sum_{i=1}^N x_i \beta^i=\underbrace{a_0}_{\in\A} + \beta \underbrace{\left(\sum_{i=0}^{n-1}a_{i+1}\beta^i + \sum_{i=0}^{N-1} x_{i+1} \beta^i\right)}_{=q\in\Zbeta}\,.
    $$
\end{proof}
\end {document}