\section{Different methods in Phase 2}
\label{sec:methodsTwo}
We propose some methods which can be used in Phase~2 to construct a set $\Qwo{k}$.

The set of possible weight coefficients $\Qwo{k}$ must be a subset of the previous set of possible weight coefficients $\Qwo{(k-1)}$. It is constructed such that
$$
 w_0 + \Qw{1}{k} \subset \A + \beta \Qwo{k}\,,
$$
i.e, it is determined also by the input digit $w_0$ and the set of carries from the right $\Qw{1}{k}$. Whereas in Phase~1 the constructed set $\Q_{k+1}$ is extended from $\Q_k$, now we  reduce the set $\Qwo{(k-1)}$ to obtain $\Qwo{k}$. Set 
$$
D_x:= \left\{q_0\in\Qwo{(k-1)}\colon\, \exists \, a\in\A: x=a+\beta q_0 \right\}\,,
$$
where $x\in w_0 + \Qw{1}{k}$, and 
$$D:=\left\{D_x\colon x\in w_0 + \Qw{1}{k}\right\}\,.$$
 The goal is to find $\Qwo{k}$ such that $D_x \cap \Qwo{k} \neq \emptyset$ for all $x\in w_0 + \Qw{1}{k}$. In other words, if at least one element of each covering sets $D_x\in D$ is contained in $\Qwo{k}$, then 
$$
 w_0 + \Qw{1}{k} \subset \A + \beta \Qwo{k}\,.
$$
We follow Algorithm~\ref{alg:minimalSet} now. Choice of possible weight coefficients set starts with $\Qwo{k}':=\emptyset$. We add the elements of all $D_x\in D$ such that $\#D_x=1$ to $\Qwo{k}'$. We remove from covering set $D$ all sets $D_x\in D$ such that $\Qwo{k}' \cap D_x \neq \emptyset$. 

Next, while $D$ is nonempty, we pick an element $q$ from $\bigcup D$ according to a chosen method, we add $q$ to $\Qwo{k}'$ and we remove all sets $D_x$ which contain $q$ from $D$. Finally, the possible weight coefficient set $\Qwo{k}=\Qwo{k}'$ is found.

Before we explain different methods  to pick an element from $\bigcup D$, we define a linear order on $\Zomega$.

\begin{defn}
\label{def:lexicographical}
Let $n$ be a positive integer. Let $(x_1, \dots, x_n)$ and $(y_1, \dots, y_n)$ be elements of $\ZZ^n$. We say that  $(x_1, \dots, x_n)$ is \emph{lexicographically smaller} than $(y_1, \dots, y_n)$, denoted by $(x_1, \dots, x_n)\preceq (y_1, \dots, y_n)$, if 
$$
x_1<y_1 \text{ or } \left(x_1=y_1 \wedge (x_2, \dots, x_n)\preceq (y_2, \dots, y_n)\right)\,.
$$
If $x$ and $y$ are elements of $\Zomega$, then we say that $x$ is \emph{lexicographically smaller} than $y$ if
$$
\pi(x) \preceq \pi(y)\,.
$$

\end{defn}
Roughly speaking, elements of $\Zomega$ are first ordered according their coefficient  of $1$, then of $\omega$, then of $\omega^2$, etc.

Algorithm~\ref{alg:pickElement} outlines methods 2a, 2b, 2c, 2d and 2d. All methods select a set $T$ of elements of $\bigcup D = \{D_x \colon D_x \in D\}$. If there is more than one element in $T$, then the lexicographically smallest element is picked.

Method 2a computes the point of gravity $g$ of elements of $\bigcup D$ considered as complex numbers. The set $T$ are elements of  $\bigcup D$ which are closest to $g$ in absolute value. 

For remaining methods, set
$$D':=\left\{D_x \in D \colon \#D_x=\min_{D_x\in D} \#D_x \right\}\,.$$
Method 2b computes the point of gravity $g$ of already picked elements $\Qwo{k}'$ considered as complex numbers. The set $T$ are elements of  $\bigcup D'$ which are closest to $g$ in absolute value. 

Methods 2c, resp. 2d, builds the set $T$ to be the smallest elements of  $\bigcup D'$ in absolute value, resp.  $\beta$-norm. 

Method 2e computes the number $n_q$ of $D_x\in D$ such that $q\in D_x$ for each $q \in \bigcup D$. The set $T$ consists of elements $q$ such that $n_q=n$ which are closest to $g$ in absolute value, where $g$ is again the point of gravity of already picked elements $\Qwo{k}'$ and $n=\max\{n_q\colon q\in \bigcup D\}$.

The motivation of these methods is to obtain the set $\Qwo{k}$ small and ``compact'' as it should be easier to cover it in the next iteration of Phase~2 (for $k+1$). Moreover, methods 2b, 2c and 2d prefer elements from the smallest covering sets $D_x$ in the hope that the picked elements are also in the bigger covering sets. Method 2e takes first elements which covers the most of the sets $D_x$.

Other experimental methods can be found in the source code. 

\begin{algorithm}
  \caption{Search for set $\Qwo{k}$ }
    \label{alg:minimalSet}
  \begin{algorithmic}[1]
    \REQUIRE{Input digit $w_0$, set of possible carries $\Qw{1}{k}$, previous set of possible weight coefficients $\Qwo{(k-1)}$}
    \STATE $D:=\{\emptyset\}$
    \FORALL{$x \in w_0 + \Qw{1}{k}$}
    	\STATE $D_x:= \{q_0\in\Qwo{(k-1)}\colon\, \exists \, a\in\A: x=a+\beta q_0 \}$
        \STATE Add $D_x$ to $D$
    \ENDFOR
    \STATE $\Qwo{k}':=\emptyset$
    \FORALL{$D_x\in D$}
    	\IF {$\#D_x=1$}
    		\STATE Add the element $q\in D_x$ to $\Qwo{k}'$
	        \STATE Remove sets $D_{x'}$ such that $q \in D_{x'}$  from the set $D$ 
	    \ENDIF
	\ENDFOR
    \WHILE{$D\neq\emptyset$}
        \STATE By Algorithm~\ref{alg:pickElement},  pick an element $q$ from $\bigcup D$
        \STATE Add the element $q$ to $\Qwo{k}'$
        \STATE Remove sets $D_x$ such that $q \in D_x$  from the set $D$ 
    \ENDWHILE
	\STATE $\Qwo{k}:=\Qwo{k}'$
    \RETURN $\Qwo{k}$
  \end{algorithmic}
\end{algorithm}


\begin{algorithm}
   \caption{Choose one element from the set of covering $D$ }
   \label{alg:pickElement}   
  \begin{algorithmic}[1]
    \REQUIRE{set of coverings $D$, method number $M\in\{$2a, 2b, 2c, 2d, 2e$\}$, already added elements $\Qwo{k}'$}
    \IF {$M=$2a}
    	\STATE $g:=$ point of gravity of elements of $\bigcup D$ as complex numbers
    	\STATE $T:=$ elements of $\bigcup D$ which are closest to $g$ in absolute value
    \ELSIF {$M\in\{$2b, 2c, 2d$\}$}
    	\STATE $m:=\min\{\#D_x \colon D_x\in D \}$
    	\STATE $D':=\{D_x \in D \colon \#D_x=m\}$
    	\IF {$M=$ 2b}
    		\STATE $g:=$ point of gravity of elements of $\Qwo{k}'$ as complex numbers
    		\STATE $T:=$ elements of $\bigcup D'$ which are closest to $g$ in absolute value
		\ELSIF {$M=$ 2c}
			\STATE $T:=$ elements of $\bigcup D'$ which are smallest in absolute value
    	\ELSIF {$M=$ 2d}
			\STATE $T:=$ elements of $\bigcup D'$ which are smallest in $\beta$-norm
    	\ENDIF
    \ELSIF {$M=$ 2e}
    	\STATE $n_q:=\#\{D_x\in D\colon q\in D_x\}$ for all $q\in \bigcup D$
    	\STATE $n=\max\{n_q\colon q\in \bigcup D \}$
    	\STATE $g:=$ point of gravity of elements of $\Qwo{k}'$ as complex numbers
    	\STATE $T:=$ elements of $\{q \in \bigcup D \colon n_q=n\}$ which are closest to $g$ in absolute value
    \ENDIF    
    \RETURN the lexicographically smallest element of $T$ according to Definition~\ref{def:lexicographical}

  \end{algorithmic}
\end{algorithm}


