\label{sec:convergencePhase2}

We have no simple sufficient or necessary condition for convergence of Phase~2 on properties of a base $\beta$ or an alphabet $\A$. Nevertheless, the non-convergence can be controled during a run of algorithm. An easy check of non-convergence can be done by finding $\Q_{[b, \dots, b]}$ for each $b\in\B$ separately. This was already described in \cite{vu}, but we recall it in this section with a simpler proof. For its purposes, we introduce a notion of stable Phase~2, which is used also in the main result of this section -- the control of non-convergence during Phase 2 is transformed into searching for a cycle in a directed graph.

Firstly, we mention some equivalent conditions of non-convergence of Phase~2. 
\begin{lem}
\label{lem:equivalentStatementsForNonConvergenePhaseTwo}
The following statements are equivalent:
\begin{enumerate}[i)]
	\item Phase~2 does not converge,
	\item $\forall \,k\in \NN \,\exists\, \tupleo{k}\in\B^{k+1} \colon \#\Qwo{k}\geq 2$,
	\item $\exists \,(w_{-j})_{j\geq 0}, w_{-j}\in\B \,\exists\, k_0\forall k\geq k_0 \colon \#\Qwo{k}=\#\Qwo{(k-1)}\geq 2$.
\end{enumerate}
\end{lem}
\begin{proof}
\textit{i)}$\iff$\textit{ii):} The while loop in Algorithm~\ref{alg:weightFunction} ends if and only if there exist $k\in\NN$ such that $\#\Qwo{k}=1$ for all $\tupleo{k}\in\B^{k+1}$.

\textit{ii)}$\iff$\textit{iii):} There is an infinite sequence $(w_{-k})_{k\geq 0}$ such that $\#\Qwo{k}\geq 2$ for all $k\in\NN$ since $\Qwo{k}\supset\Qwo{(k+1)}$. Hence, the sequence of integers $(\#\Qwo{k})_{k\geq 0}$ is eventually constant. The opposite implication is trivial.
\end{proof}

We need to ensure that choice of a possible weight coefficient set $\Qwo{k}\subset \Qwo{(k-1)}$ is determined by an input digit $w_0$ and a set $\Qw{1}{0}$, while the influence of the set $\Qwo{(k-1)}$ is limited. It is formalized in the following definition.

\begin{defn}
Let $\B$ be an alphabet of input digits. We say that Phase~2 is \emph{stable} if 
$$
\Qw{1}{k}=\Qw{1}{(k-1)} \implies \Qwo{k}=\Qwo{(k-1)}
$$
for all $k\in\NN, k\geq 2$ and for all $\tupleo{(k+1)} \in \B^{k+1}$.

%\komentar{ii)$\#\Qw{1}{k}=1 \implies \#\Qwo{k}=1$, neni potreba pokud nebude opacna implikace}
\end{defn}
The definition may seem too restrictive, but note that $\Qwo{k}$ if fully determined by $\Qw{1}{k}$, $\Qwo{(k-1)}$ and $w_0$ for a fixed deterministic way of choice of possible weight coefficients sets. Therefore, the assumption $\Qw{1}{k}=\Qw{1}{(k-1)}$, i.e. carries from the right are same, implies that the only difference in the choice of $\Qwo{k}$ an $\Qwo{(k-1)}$ is that $\Qwo{k}$ is a subset of  $\Qwo{(k-1)}$, while $\Qwo{(k-1)}$ is chosen as a subset of $\Qwo{(k-2)}$. At the same time, $\Qwo{(k-1)}$ is a subset of $\Qwo{(k-2)}$. Thus, the property that Phase~2 is stable means that the same possible weight coefficients set is found even if it is constructed as a subset of smaller set. This is natural way how an algorithm of choice should be constructed -- the set $\Qwo{k}$ is constructed such that
$$
\B+\Qw{1}{k} \subset \A+\beta \Qwo{k}\,,
$$
i.e., there is no reason to choose the set $\Qwo{k}$ to be a proper subset of $\Qwo{(k-1)}$ as we know that
$$
\B+\underbrace{\Qw{1}{(k-1)}}_{=\Qw{1}{k}} \subset \A+\beta \Qwo{(k-1)}\,,
$$
and $\Qw{1}{(k-1)}$ was chosen as sufficient.
In other words, if $\Qwo{k}\subsetneq\Qwo{(k-1)}$, the set $\Qwo{(k-1)}$ might have been chosen better. 

We may guarantee that Phase~2 is stable by wrapping the choice of the set $\Qwo{k}$ into a simple while loop, see Algorithm~\ref{alg:possibleWeightCoefSetStable} in Chapter~\ref{chap:design}.

Now we use that finiteness of Phase~2 implies that there exists a length of window $m$ such that the set $\Qb{m}$ contains only one element for all $b\in\B$, where $\Qb{m}$ is a shorter notation for
$$
\Q_{[\underbrace{\scriptstyle b,\dots,b}_m]}\,.
$$
The following theorem was proved in \cite{vu} with the assumption that Phase~2 is deterministic. Briefly, it says that $\#\Qb{m}$ must decrease every time we increase $m$, otherwise Phase~2 does not converge. When we consider only inputs of the form $bb\dots b$ for some $b\in\B$, determinism implies that Phase~2 is stable. The given proof with Phase~2 being stable is slightly shorter.

\begin{thm}
\label{thm:bbbCondition}
Let $m_0 \in \NN$ and $b\in\B$ be such that sets $\Qb{m_0}$ and $\Qb{m_0-1}$ produced by stable Phase~2 have the same size. Then
$$
    \#\Qb{m} = \#\Qb{m_0} \qquad \forall m\geq m_0-1\,.
$$ 
Particularly, if $\#\Qb{m_0}\geq 2$, Phase~2 does not converge.
\end{thm}
\begin{proof}
As $\Qb{m_0} \subset \Qb{m_0-1}$, the assumption of the same size implies
$$
    \Qb{m_0} = \Qb{m_0-1}\,.
$$
By the assumption that Phase~2 is stable, we have
\begin{align*}
 \Qb{m_0} = \Qb{m_0-1} &\implies  \Qb{m_0+1} = \Qb{m_0} \\
 						&\implies  \Qb{m_0+2} = \Qb{m_0+1} \\
 						&\vdots
\end{align*}
This implies the statement.

If $\#\Qb{m_0}\geq 2$, then the statement \textit{iii)} in Lemma~\ref{lem:equivalentStatementsForNonConvergenePhaseTwo} holds for the sequence $(b)_{k\geq 0}$.
\end{proof}



The condition of non-convergence during Phase~2 is formulated as a searching for an infinite path in a so-called Rauzy graph.
\begin{defn}
Let $\B$ be an alphabet of input digits. Let Phase~2 be stable. Let $k\in\NN, k\geq 2$. We set
$$
V:=\left\{\tuple{1}{k}\in\B^k \colon \#\Qw{1}{k}=\#\Qw{1}{(k-1)}\right\}
$$
and
$$
E:=\left\{\tuple{1}{k}\rightarrow\tuple[w']{1}{k}\in V\times V \colon \tuple{2}{k}=\tuple[w']{1}{(k-1)}\right\}\,.
$$
The directed graph $G_k=(V,E)$ is called \emph{Rauzy graph of Phase~2 (for the window of length~$k$)}.
\end{defn}
 This term comes from combinatorics on words. The vertices of our graph are combinations of input digits for which the size of their possible weight coefficients sets did not decrease with an increment of length of the window. Whereas in combinatorics on words, vertices are given as factors of some language. But the directed edges are placed in the same manner -- if some combination of digits without the first digit equals another combination without the last digit.

The structure of Rauzy graph $G_k$ signifies whether the non-decreasing combinations are such that they cause non-convergence of Phase~2. Existence of an infinite walk in $G_k$ implies that Phase~2 does not converge:

\begin{thm}
\label{thm:infinitePathInRauzyGraph}
Let Phase~2 is stable.  If there exists $k_0\in\NN, k_0\geq 2$, and $\tupleo{k_0}\in\B^{k_0+1}$ such that
\begin{enumerate}[i)]
	\item $\#\Qwo{(k_0-1)}>1$ and
	\item there exists an infinite walk $(\tuple[w^{(i)}]{1}{k_0})_{i\geq 1}$ in $G_{k_0}$ which starts in the vertex  $$\tuple[w^{(1)}]{1}{k_0}=\tuple{1}{k_0}\,,$$ 
\end{enumerate}
then Phase~2 does not converge.
\end{thm}
\begin{proof}
Set
$$(w_k)_{k\geq 0}:=w_0, w_1^{(1)}, \dots , w^{(1)}_{k_0-1}, w^{(1)}_{k_0}, w_{k_0}^{(2)},w_{k_0}^{(3)},w_{k_0}^{(4)},\dots$$
We prove that $\#\Qwo{k}=\#\Qwo{(k_0-1)}>1$ for all $k\geq k_0-1$, i.e., the condition \textit{iii)} in Lemma~\ref{lem:equivalentStatementsForNonConvergenePhaseTwo} is satisfied.

%The general ideas of the proof are following: if $\tuple[w']{1}{k_0}$ is a vertex of $G_{k_0}$, then $$\Qw[w']{1}{(k_0-1)}=\Qw[w']{1}{k_0}\,.$$ And the assumption that Phase~2 is stable implies that $$\Qw[w']{1}{(k_0-1)}=\Qw[w']{1}{k_0}\implies \Qwo[w']{(k_0-1)}=\Qwo[w']{k_0}$$ for all $w'_0\in\B$.

%Now we show that $\Qwo{k}=\Qwo{(k+1)}$ for all $k\geq k_0-1$. 
Let $\ell\in\NN$. Since $\tuple{(1+\ell)}{(k_0+\ell)}$ is a vertex of $G_{k_0}$, the set $\Qw{\ell}{(k_0+\ell)}$ equals $\Qw{\ell}{(k_0+\ell-1)}$. As Phase~2 is stable, we have
\begin{align*}
\Qw{\ell}{(k_0+\ell)}&=\Qw{\ell}{(k_0+\ell-1)}\\
\implies \Qw{(\ell-1)}{(k_0+\ell)}&=\Qw{(\ell-1)}{(k_0+\ell-1)}\\
&\vdots \\
\implies \Qw{1}{(k_0+\ell)}&=\Qw{1}{(k_0+\ell-1)}\\
\implies \Qwo{(k_0+\ell)}&=\Qwo{(k_0+\ell-1)}\,.
\end{align*}
Hence, $\#\Qwo{k}=\#\Qwo{(k_0-1)}>1$ for all $k\geq k_0-1$.
\end{proof}
%\komentar{bylo by fajn dokazat i opacny smer, jedine, pres co se neumim dostat je kdyby existovala jen aperiodicka posloupnoust, kvuli ktere to nekonverguje}



We remark that existence of an infinite walk in a finite graph is equivalent to existence of a cycle in the graph. Thus, if there is an infinite walk, we may find another one whose sequence of vertices is eventually periodic. We use this fact in Section~\ref{sec:modifiedPhase2} which describes modified algorithm for Phase~2 which implements the result of Theorem~\ref{thm:infinitePathInRauzyGraph}.









