\documentclass[24pt, a0paper, portrait, margin=0mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=-5mm]{tikzposter}
\tikzposterlatexaffectionproofoff



\usepackage{tabulary}
\usepackage{caption}
\input{../commands.tex}

\title{Construction of algorithms for parallel addition} 
\author{Jan Legersk\'y, Czech Technical University in Prague} 
%\institute{Czech Technical University in Prague}


\definecolorstyle{Czech} {
\definecolor{colorOne}{HTML}{34888C}%116699
\definecolor{colorTwo}{HTML}{C1E1DC}
\definecolor{colorThree}{HTML}{FFF2BE}
%\definecolor{colorOne}{HTML}{34888C}%116699
%\definecolor{colorTwo}{HTML}{7CAA2D}
%\definecolor{colorThree}{HTML}{F5E356}
%\definecolor{colorOne}{HTML}{4F6457}%116699
%\definecolor{colorTwo}{HTML}{D9B44A}
%\definecolor{colorThree}{HTML}{ACD0C0}
%\definecolor{colorOne}{HTML}{0D5078}%116699
%\definecolor{colorTwo}{HTML}{A2C4D9}
%\definecolor{colorThree}{HTML}{FCF0AD}
}{
     % Background Colors
    \colorlet{backgroundcolor}{colorTwo}
    \colorlet{framecolor}{colorThree}
    % Title Colors
    \colorlet{titlebgcolor}{colorOne}
    \colorlet{titlefgcolor}{white}
    % Block Colors
    \colorlet{blocktitlebgcolor}{white}
    \colorlet{blocktitlefgcolor}{colorOne}
    \colorlet{blockbodybgcolor}{white}
    \colorlet{blockbodyfgcolor}{black}
    % Innerblock Colors
    \colorlet{innerblocktitlebgcolor}{white}
    \colorlet{innerblocktitlefgcolor}{black}
    \colorlet{innerblockbodybgcolor}{colorThree}
    \colorlet{innerblockbodyfgcolor}{black}
    % Note colors
    \colorlet{notefgcolor}{black}
    \colorlet{notebgcolor}{colorThree}
    \colorlet{notefrcolor}{colorThree}
}


\usebackgroundstyle{Default} %Rays
\usetitlestyle{Filled}
\usecolorstyle{Czech}

\useblockstyle[bodyoffsety=12mm]{Slide}
\usenotestyle{Default}



\settitle{ \centering \vbox{
%\@titlegraphic\\[\TP@titlegraphictotitledistance] 
\centering
\color{titlefgcolor} {\bfseries \Huge \sc \@title \par}
\vspace*{1em}
{\huge \@author \par}% \vspace*{1em} {\LARGE \@institute}
}}


\renewcommand{\Qw}[3][w]{\Q_{[#1_{j-#2}, \dots, #1_{j-#3}]}}
\renewcommand{\Qwo}[2][w]{\Q_{[#1_{j}, \dots, #1_{j-#2}]}}

\renewcommand{\tuple}[3][w]{(#1_{j-#2}, \dots, #1_{j-#3})}
\renewcommand{\tupleo}[2][w]{(#1_{j}, \dots, #1_{j-#2})}




\begin{document}
\maketitle[titletoblockverticalspace=15mm]
\begin{columns} 
\column{0.4}
\block{Abstract}{
Parallel addition is used for example in fast division algorithms with an integer base and alphabet.  An extending window method, which is due to M. Svobodov\'a, attempts to construct parallel addition algorithms in more general numeration systems. 

We discuss the sucessfulness of the method based on given parameters and we develop tools to reveal failure. 

Besides theoretical results, we implemented the method with several inner modifications in SageMath. The easy control of failure allowed to test more than 5000 different numeration systems to obtain a parallel addition algorithm in about 120 cases.
}

\input{numSystem.tex}
\input{addition.tex}
\input{conversion.tex}
\input{parallelStandard.tex}
\input{alphabet.tex}

\note[targetoffsetx=0cm,targetoffsety=11pt,innersep=0.5cm,angle=-90, width=\colwidth]{\url{jan.legersky@gmail.com}, \url{github.com/Legersky/ParallelAddition}}
%\block{}{}

\column{0.6}
\input{ewm.tex}



\begin{subcolumns}
\subcolumn{0.43}
\input{phase1.tex}
\input{phase2img.tex}
\subcolumn{0.57}
\input{phase1img.tex}
\input{phase2.tex}
\end{subcolumns}

\input{phase1convergence.tex}

%\begin{subcolumns}
%\subcolumn{0.5}
%
%
%\subcolumn{0.5}
%
%
%\end{subcolumns}


\input{phase2convergence.tex}
\input{examples.tex}


\block{}{
C.~Frougny, E.~Pelantov\'a, and M.~Svobodov\'a, \emph{Parallel addition in
  non-standard numeration systems}, Theoret. Comput. Sci. \textbf{412} (2011),
  5714--5727.

%C.~Frougny, E.~Pelantov{\'a}, and M.~Svobodov{\'a}, \emph{Minimal digit sets
%  for parallel addition in non-standard numeration systems}, J. Integer Seq.
%  \textbf{16} (2013), 36.
}


\end{columns}
%\center KM FJFI \v{C}VUT, Trojanova 13, 120 00 Praha 2, Czech Republic,  \url{jan.legersky@gmail.com}
\end{document}


